Classless Java

### 2015-11-10 paper/sections/RelatedWork.tex
Notes added

\subsection{ThisType/MyType/Extensibility}
Typical object-oriented programming languages (e.g. Java) use class names as
types and inheritance as subtyping relations. This gives difficulty when
extending classes/interfaces with recursive types. Problems such as binary
methods, return type refinement, etc. emerge and hinders software extensibility
greatly.

>>>>

\subsection{ThisType/MyType/Extensibility}
\marco{ this section is unfair. There are unsolved problems with ThisType in negative positions, namelly it breaks subtyping. The most common solution is to allow calling some methods only when the exact type is known. This demolish most advantages of interfaces.}
Typical object-oriented programming languages (e.g. Java) use class names as
types and inheritance as subtyping relations. This gives difficulty when
extending classes/interfaces with recursive types. Problems such as binary
methods, return type refinement, etc. emerge and hinders software extensibility
greatly.
